A quantum parallel Markov chain Monte Carlo

### 2022-09-26 main.tex
small edits plus kth rank experiment

We propose a novel quantum computing strategy for \emph{parallel MCMC} algorithms that generate multiple proposals at each step. This strategy makes parallel MCMC amenable to quantum parallelization by using the Gumbel-max trick to turn the generalized accept-reject step into a discrete optimization problem.  When combined with new insights from the parallel MCMC literature, such an approach allows us to embed target density evaluations within a well-known extension of Grover's quantum search algorithm.  Letting $P$ denote the number of proposals in a single MCMC iteration, the combined strategy reduces the number of target evaluations required from $\order{P}$ to $\order{P^{1/2}}$.  In the following, we review the rudiments of quantum computing, quantum search and the Gumbel-max trick in order to elucidate their combination for as wide a readership as possible.

@@

This work leads to two interesting questions.   First, what is the status of inference obtained by QPMCMC?  The QPMCMC selection step relies on quantum minimization, an algorithm that only achieves success with probability $1-\epsilon$.  While empirical studies suggest that this error induces little bias, it would be helpful to use this $\epsilon$ to bound the distance between the target distribution and the distribution generated by QPMCMC.  Such theoretical efforts would need to extend recent formalizations of the parallel MCMC paradigm \textcolor{red}{CITATION} to account for biased MCMC kernels.

>>>>

We propose a novel quantum computing strategy for parallel MCMC algorithms that generate multiple proposals at each step. This strategy makes parallel MCMC amenable to quantum parallelization by using the Gumbel-max trick to turn the generalized accept-reject step into a discrete optimization problem.  When combined with new insights from the parallel MCMC literature, such an approach allows us to embed target density evaluations within a well-known extension of Grover's quantum search algorithm.  Letting $P$ denote the number of proposals in a single MCMC iteration, the combined strategy reduces the number of target evaluations required from $\order{P}$ to $\order{P^{1/2}}$.  In the following, we review the rudiments of quantum computing, quantum search and the Gumbel-max trick in order to elucidate their combination for as wide a readership as possible.

@@

This work leads to two interesting questions.   First, what is the status of inference obtained by QPMCMC?  The QPMCMC selection step relies on quantum minimization, an algorithm that only achieves success with probability $1-\epsilon$.  While empirical studies suggest that this error induces little bias, it would be helpful to use this $\epsilon$ to bound the distance between the target distribution and the distribution generated by QPMCMC.  Such theoretical efforts would need to extend recent formalizations of the multiproposal based parallel MCMC paradigm \citep{glatt} to account for biased MCMC kernels.
